Predicting computational reproducibility of scientific pipelines using collaborative filtering

### 2018-04-19 paper.tex
Updates following meeting with Soudabeh

\subsection{Sampling the Training Set}

@@

% 3. rows
\paragraph{Complete Rows} The training set is sampled by selecting complete 
rows in the matrix, that is, the first files produced by
every execution. The last selected row might be incomplete to meet the
exact training ratio. This method is realistic: it corresponds to a 
situation where the processing of all the subjects is launched and 
interrupted before the execution is complete. The collaborative 
filtering method will then predict the reproducibility of the remaining 
files. Figure~\ref{fig:Rows-Sample-Training-set} represents a training 
set sampled using this method.
\begin{figure}[h!]
	\centering
	\begin{subfigure}[b]{0.6\linewidth}
		\includegraphics[width=\columnwidth]{figures/5vs7_random-unreal_04_training}
  		\caption{Random Unreal method}
  		\label{fig:Random-Unreal-Sample-Training-set}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
  		\includegraphics[width=\columnwidth]{figures/5vs7_columns_04_training}
  		\caption{Complete Columns method}
  		\label{fig:Columns-Sample-Training-set}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
  		\includegraphics[width=\columnwidth]{figures/5vs7_rows_04_training}
  		\caption{Complete Rows method}
  		\label{fig:Rows-Sample-Training-set}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
 		\includegraphics[width=\columnwidth]{figures/5vs7_random-real_04_training}
		\caption{Random Subjects method}
  		\label{fig:Uniform-S-Sample-Training-set}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
  		\includegraphics[width=\columnwidth]{figures/5vs7_diagonal_04_training}
  		\caption{(Uniform) method }
  		\label{fig:Diagonal-Sample-Training-set}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
  		\includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-largest_04_training}
  		\caption{(Triangular-L) method}
  		\label{fig:triangular-L-Sample-Training-set}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
  		\includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-smallest_04_training}
  		\caption{(Triangular-S) method}
  		\label{fig:triangular-S-Sample-Training-set}
	\end{subfigure}
	\caption{Sample training set for different methods with a training ratio of 0.4.}		
\end{figure}

\paragraph{Random Subjects- RS} This method builds the 
training set by selecting the next generated file of a random subject 
until the training ratio is reached. The next generated file of a 
subject is the file with the lowest index in this subject that has not 
been already selected in the training set. This method is realistic as 
files are sampled according to their production timestamps. 
Figure~\ref{fig:Uniform-S-Sample-Training-set} represents a training 
set sampled using this method.

\paragraph{Random File Numbers (Uniform)- RFNU}
The number of files selected for every subject is randomly selected in a 
uniform distribution with parameters \textit{\textbf{a}} and \textit{\textbf{b}} where \textit{\textbf{a}} and \textit{\textbf{b}} are set as follows:\\
\textit{\textbf{a}} : The minimume random of file index that could be selected for a subject\\ 
\textit{\textbf{b}} : The highest possibility of file index that could be selected for a subject\\
$\mathbf{\alpha}$ : Training ratio\\
\textit{\textbf{Nf}} : Index file which means all files with lower and equal to this number should be sampled into the training set.
This method is realistic as files are sampled according to their production timestamps.
Due to sampling issues, it is possible that the actual training ratio obtained with this method
does not match the target one. We check that the difference between the target and real training ratios
was lower than 0.01.

\paragraph{Random File Numbers (Triangular)- RFNT}
The number of files selected in every subject is randomly selected in a triangular distribution
with parameters a, b and c where a, b and c are set as follows: \ldots{}
This ununiform distribution aims at sampling files produced towards the end of the execution.
Two approches are tried to apply this method:
\begin{enumerate}
\item Largest-a (RFNT-L):  In this approach there is a concern to eliminate the possibility of having less \todo{Reformulate, this is unclear.}
than the two first generated files of any subjects in the sampled training set. 
The possibility of missing some subjects in training set can happen to some of them due to 
random selection of subjects or even meeting the determined training ratio before 
having the chance of being selected.

@@

\subsection{ALS without biases}
Results show that in all condition pairs Complete Columns method has 
almost a constant accuracy even if the training ratio increased and it 
is almost two times less than dummy classifier in more differentiated 
condition pairs (CentOS5 vs CentOS7 and CentOS6 vs CentOS7). But in the 
best case which it means in similar conditions the Complete Columns 
accuracy is as much accurate as the Dummy classifier which is $0.65$ 
percent Figure~\ref{fig:columns method} represents
the ROC curves of Complete Columns method with comparision to dummy 
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.3\linewidth}
                \includegraphics[width=\columnwidth]{figures/columns_5vs6}
        \end{subfigure}
        \begin{subfigure}[b]{0.3\linewidth}
                \includegraphics[width=\columnwidth]{figures/columns_5vs7}
        \end{subfigure}
        \begin{subfigure}[b]{0.3\linewidth}
                \includegraphics[width=\columnwidth]{figures/columns_6vs7}
        \end{subfigure}
        \caption{Average performance of Complete Columns methods in three different condition pairs}
        \label{fig:columns method}
\end{figure}
In general the accuracy pattern of the two Complete Rows and 
RS methods show similar decline and grow behavior over the 
training ratio axis however it can be subject to considerable 
fluctuations in differentiated condition pairs. Dispite of their 
likely irrational behaviour, they always have better accuracy 
for the training size with less than $0.3$ in comparison to other 
methods. This better performance (around 75 percent)is almost three 
times higher than other methods in condition pairs with more 
differences but just 20 percent better when the conditions are more 
similar to each other (CentOS5 vs CentOS6) with accuracy of $90\%$.
Figure~\ref{fig:RS_Rows} represents
the ROC curves of these two methods with comparision to dummy
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/RS_Rows_5vs6}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/RS_Rows_5vs7}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/RS_Rows_6vs7}
        \end{subfigure}
        \caption{Average performance of RS and Complete Rows methods in three different condition pairs}
        \label{fig:RS_RowS}
\end{figure}

>>>>

\subsection{Sampling the training set}

@@

% 3. rows
\paragraph{Complete Rows} The training set is sampled by selecting complete 
rows in the matrix, that is, the first files produced by
every execution. The last selected row might be incomplete to meet the
exact training ratio. This method is realistic: it corresponds to a 
situation where the processing of all the subjects is launched and 
interrupted before the execution is complete. The collaborative 
filtering method will then predict the reproducibility of the remaining 
files. Figure~\ref{fig:Rows-Sample-Training-set} represents a training 
set sampled using this method.
\begin{figure}[h!]
	\centering
	\begin{subfigure}[b]{0.4\linewidth}
		\includegraphics[width=\columnwidth]{figures/5vs7_random-unreal_04_training}
  		\caption{Random Unreal method}
  		\label{fig:Random-Unreal-Sample-Training-set}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
  		\includegraphics[width=\columnwidth]{figures/5vs7_columns_04_training}
  		\caption{Complete Columns method}
  		\label{fig:Columns-Sample-Training-set}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
  		\includegraphics[width=\columnwidth]{figures/5vs7_rows_04_training}
  		\caption{Complete Rows method}
  		\label{fig:Rows-Sample-Training-set}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
 		\includegraphics[width=\columnwidth]{figures/5vs7_random-real_04_training}
		\caption{Random Subjects method}
  		\label{fig:Uniform-S-Sample-Training-set}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
  		\includegraphics[width=\columnwidth]{figures/5vs7_diagonal_04_training}
  		\caption{(Uniform) method }
  		\label{fig:Diagonal-Sample-Training-set}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
  		\includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-largest_04_training}
  		\caption{(Triangular-L) method}
  		\label{fig:triangular-L-Sample-Training-set}
	\end{subfigure}
	\begin{subfigure}[b]{0.4\linewidth}
  		\includegraphics[width=\columnwidth]{figures/5vs7_random-triangular-smallest_04_training}
  		\caption{(Triangular-S) method}
  		\label{fig:triangular-S-Sample-Training-set}
	\end{subfigure}
	\caption{Sample training set for different methods with a training ratio of 0.4.}		
\end{figure}

\paragraph{Random Subjects -- RS} This method builds the 
training set by selecting the files from random subjects 
until the training ratio is reached. The file selected in a 
subject is the file with the lowest index in this subject that has not 
been already selected in the training set. This method is realistic as 
files are sampled according to their production timestamps. 
Figure~\ref{fig:Uniform-S-Sample-Training-set} represents a training 
set sampled using this method.

\paragraph{Random File Numbers (Uniform) -- RFNU}

The number of files selected for every subject is randomly selected in 
a uniform distribution with parameters \textit{\textbf{a}} and 
\textit{\textbf{b}} where \textit{\textbf{b}} is set to the total 
number of files $N_{f}$ and \textit{\textbf{a}} is set such that the 
distribution average equals to $\alpha N_{f}$ where $\alpha$ is the training ratio,  that is, 
$\textit{\textbf{a}}=(2\alpha-1)N_{f}$. \todo{Explain what you do when alpha is lower than 0.5}

This method is realistic as files are sampled according to their production timestamps.
Due to sampling issues, it is possible that the actual training ratio obtained with this method
does not match the target one. We check that the difference between the target and real training ratios
was lower than 0.01.

\paragraph{Random File Numbers (Triangular) -- RFNT}
The number of files selected in every subject is randomly selected in a triangular distribution
with parameters a, b and c where a, b and c are set as follows: \ldots{}
This distribution aims at sampling files produced towards the end of the execution.
Two approches are tried to apply this method:
\begin{enumerate}
\item Largest-a (RFNT-L):  In this approach there is a concern to eliminate the possibility of having less \todo{Reformulate, this is unclear.}
than the two first generated files of any subjects in the sampled training set. 
The possibility of missing some subjects in training set can happen to some of them due to 
random selection of subjects or even meeting the determined training ratio before 
having the chance of being selected.

@@

\subsection{ALS without biases}

\todo{1. Use the same ordering and paragraph headings as in the method 
section. 2. Don't mix multiple ideas/results in the same paragraph. 3. 
Mention and describe the figure before discussing it.}

Results show that in all condition pairs Complete Columns method has 
almost a constant accuracy even if the training ratio increased and it 
is almost two times less than dummy classifier in more differentiated 
condition pairs (CentOS5 vs CentOS7 and CentOS6 vs CentOS7). But in the 
best case which it means in similar conditions the Complete Columns 
accuracy is as much accurate as the Dummy classifier which is $0.65$ 
percent Figure~\ref{fig:columns method} represents
the ROC curves of Complete Columns method with comparision to dummy 
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.3\linewidth}
                \includegraphics[width=\columnwidth]{figures/columns_5vs6}
        \end{subfigure}
        \begin{subfigure}[b]{0.3\linewidth}
                \includegraphics[width=\columnwidth]{figures/columns_5vs7}
        \end{subfigure}
        \begin{subfigure}[b]{0.3\linewidth}
                \includegraphics[width=\columnwidth]{figures/columns_6vs7}
        \end{subfigure}
        \caption{Average performance of Complete Columns methods in three different condition pairs}
        \label{fig:columns method}
\end{figure}
In general the accuracy pattern of the two Complete Rows and 
RS methods show similar decline and grow behavior over the 
training ratio axis however it can be subject to considerable 
fluctuations in differentiated condition pairs. Dispite of their 
likely irrational behaviour, they always have better accuracy 
for the training size with less than $0.3$ in comparison to other 
methods. This better performance (around 75 percent)is almost three 
times higher than other methods in condition pairs with more 
differences but just 20 percent better when the conditions are more 
similar to each other (CentOS5 vs CentOS6) with accuracy of $90\%$.
Figure~\ref{fig:RS_Rows} represents
the ROC curves of these two methods with comparision to dummy
classifier over the increasement of the training ratio.
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/RS_Rows_5vs6}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/RS_Rows_5vs7}
        \end{subfigure}
        \begin{subfigure}[b]{0.4\linewidth}
                \includegraphics[width=\columnwidth]{figures/RS_Rows_6vs7}
        \end{subfigure}
        \caption{Average performance of RS and Complete Rows methods in three different condition pairs}
        \label{fig:RS_RowS}
\end{figure}
